% BEGIN 030.genetic.tex. Explanation of the genetic strategy used
\section{Population dynamics}\label{sec:genetic}
% Why is it impossible for us to do the simulation as a deterministic population model?

\subsection{The genetic algorithm}
The population dynamics used is a simple genetic algorithm with selection and replacement but without recombination (crossover). Let $\mu$ be the population size and $P_{t} = \{x_1, x_2, \dots, x_\mu\}$ the population at time $t$. The individual \textco{evaluation} is performed in comparison to all other individuals in the population as
\begin{equation*}
f'(x_i) = \frac{\sum_{j = 1}^\mu f_{i,j}}{\sum_{i,j = 1}^\mu f_{i, j}}
\end{equation*}
where $f_{i, j}$ is the payoff according to \ref{equ:game:payoff} for $x_i$ playing against $x_j$, $f_{i,i} = 0$.


In the \textco{parent selection} phase $\nu$ individuals are chosen to be parents, and the expected number of offspring is in proportion to the individuals fitness according to\footnote{Usually one needs to normalise the expectation, but here $f$ already is relative to the payoff sum.}
\begin{equation*}
ev(x) = \nu f(x).
\end{equation*}


\subsection{Mutation operators}
Four different mutation operators are used, two w.r.t. memory length and two w.r.t. action taken (cooperate/defect). Their function and motivation are as follows

\begin{itemize}
\item Duplication operator: This mutation duplicates a chromosome and conserves its strategy by copying a chromosome and adding it to itself.
\item Split operator: This mutation takes a chromosome a splits it in half, whereafter one part is chosen at random and kept, while the other is thrown away. In theory shorter memory strategys are covered by a longer memory and thus this operator is unnecessary, however with the large search space that is given by having a choice probability between 0 and 1 it is very unlikely that a longer memory strategy will exactly represent a shorter one.
\item Float mutation: This mutation changes the probability for cooperation by a small increment to either more probable or less probable.
\item Switch mutation: Switches the probability for a given action by making the assignment $P_{C} = 1 - P_{C}$. In the deterministic case, this corresponds to switching between cooperate and defect.
\end{itemize}



\subsection{Selection}

\subsection{Replacement}



% END 030.genetic.tex.
